Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-25 texor.Rmd
software version numbers

- \CRANpkg{texor}: https://abhi-1u.github.io/texor
- \CRANpkg{rebib}: https://abhi-1u.github.io/rebib/
- This paper: https://github.com/Abhi-1U/texor-rjarticle
- More details on \CRANpkg{rjtools} are at https://rjournal.github.io/rjtools/

>>>>

- \CRANpkg{texor}: Version 1.2.0 https://abhi-1u.github.io/texor
- \CRANpkg{rebib}: Version 0.3.0 https://abhi-1u.github.io/rebib/
- This paper: https://github.com/Abhi-1U/texor-rjarticle
- More details on \CRANpkg{rjtools} are at https://rjournal.github.io/rjtools/
